SatNOGS: Satellite~Networked~Open~Ground~Station

### 2015-08-27 paper.tex
update authors, more refs

% \IEEEauthorrefmark{1}
\author{
    \IEEEauthorblockN{Daniel J. White, Ph.D., AD\pmzeroslash CQ}
    %\IEEEauthorblockN{Daniel J. White, Ph.D., AD\O CQ}
    \IEEEauthorblockA{%
        Valparaiso University\\
        Valparaiso, Indiana\\
        \href{mailto:dan.white@valpo.edu}{dan.white@valpo.edu}}\\
    \and
    \IEEEauthorblockN{SatNOGS Developers}
    \IEEEauthorblockA{Libre Space Foundation\\
    \href{mailto:info@satnogs.org}{info@satnogs.org}}
}

@@

What is missing is a civilian infrastructure to connect these many owners and ground station operators in a way that is flexible and open.
The ESA's Global Educational Network for Satellite Operations (GENSO) \cite{GENSO} was a notable attempt at such a network aimed at University-class projects and stations.
The fact that the \verb|genso.org| domain name does not resolve to a live server is an indication of the practical current state of the project.

First proposed as a part of the 2014 International Space Apps Challenge's ``Virtual Ground Station App -- Global Crowdsourcing of CubeSats'' Challenge \cite{SpaceAppsChallenge2014-SatNOGS}, the SatNOGS project seeks to build such a network and community.
It was later submitted as an entry to the 2014 Hackaday Prize \cite{Hackaday-SatNOGS}, ultimately winning the grand prize of $\$196,418$.

% TODO:
\cite{Hackerspacegr}
\cite{Silver2015}
\cite{SatNOGS-Hamvention2015}

@@

Note, screen captures of the various software components and demonstrations are included in the more appropriate format of slides in the presentation instead of in the paper.

>>>>

% \IEEEauthorrefmark{1}
\author{
    \IEEEauthorblockN{Daniel J. White, Ph.D., AD\pmzeroslash CQ}
    %\IEEEauthorblockN{Daniel J. White, Ph.D., AD\O CQ}
    \IEEEauthorblockA{%
        Valparaiso University\\
        Valparaiso, Indiana\\
        \href{mailto:dan.white@valpo.edu}{dan.white@valpo.edu}}\\
    %\and
    \\
    \IEEEauthorblockN{%
        Ioannis Giannelos,
        Agisilaos Zissimatos,
        Eleytherios Kosmas,\\
        Dimitrios Papadeas,
        Pierros Papadeas,
        Matthaios Papamathaiou,\\
        Nikolaos Roussos,
        Vasileios Tsiligiannis,
        Ioannis Charitopoulos}
    \IEEEauthorblockA{%
        Libre Space Foundation\\
        Athens, Greece\\
    \href{mailto:info@satnogs.org}{info@satnogs.org}}
}

@@

What is missing is a civilian infrastructure to connect these many owners and ground station operators in a way that is flexible and open.
The ESA's Global Educational Network for Satellite Operations (GENSO) \cite{GENSO} was a notable attempt at such a network aimed at University-class projects and stations.
The fact that the \verb|genso.org| domain name does not resolve to a live server is practical indication of the current state of the project.

Members of \emph{Hackerspace.gr} \cite{Hackerspacegr} in Athens Greece first proposed SatNOGS as a part of the 2014 International Space Apps Challenge's ``Virtual Ground Station App -- Global Crowdsourcing of CubeSats'' Challenge \cite{SpaceAppsChallenge2014-SatNOGS}.
It was later submitted as an entry to the 2014 Hackaday Prize \cite{HackadayPrize2014}, ultimately winning the grand prize of $\$196,418$.
The funds provided seed money to start the Libre Space Foundation \cite{LibreSpaceFoundation}, a new non-profit dedicated to supporting free and open source space and related projects.

% TODO:
%\cite{Silver2015}
%\cite{SatNOGS-Hamvention2015}

@@

All code and hardware designs for the project are publicly available \cite{SatNOGS-github} under Open Software (AGPLv3 and GPLv3) and Open Hardware (CERN OHLv1.2) licenses.
Software documentation may be found at \cite{SatNOGS-docs}.
Note, screen captures of the various software components, hardware pictures, and demonstrations are included in the more appropriate format of the presentation instead of in the paper.
